CSCI 580 : Monte Carlo Path Tracing

### 2015-11-27 paper/paper.tex
explain MCPT auxiliary algorithms

\begin{description}
  \item[1)] Generate a ray from the camera (position x,y, horizontal and vertical fields of view u,v), passing through the image plane, with weight = 1
  \item[2)] Find the point of intersection with the nearest surface
  \item[3)] Randomly (Russian Roulette) decide whether the light is emitted or reflected (test against Kd or Ks)
  \item[3A)] if emitted, return weight * Le
  \item[3B)] if refleced, weight *= Ks, randomly scatter the ray according to the BRDF pdf, and go to step 2
\end{description}

>>>>

\begin{description}
  \item[1)] Generate a ray from the camera (position x,y, horizontal and vertical fields of view u,v), passing through the image plane, with weight = 1
  \item[2)] Find the point of intersection with the nearest surface
  \item[3)] Randomly (Russian Roulette) decide whether the light is emitted or reflected (test against Kd or Ks)
  \item[3A)] if emitted, return weight * Le
  \item[3B)] if refleced, weight *= Ks, randomly scatter the ray according to its BRDF pdf, and go to step 2
\end{description}

In order for this algorithm to be implemented, other algorithms such as ray-triangle intersection and Phong shading (for emitted light) must also be implemented. 
Additionally, a BRDF probability distribution function (pdf) must be created for each surface. A reasonable BRDF pdf would be a uniform distribution, wherein \emph{any} 
vector (x,y,z) which is in the hemisphere of the surface is randomly selected.
